---
title: "Text Mining FOMC"
author: "christoffer.nordenlow@outlook.com"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

<style type="text/css">
  body{
  font-size: 11pt;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(tidyverse)
library(lubridate)
library(slider)
library(dplyr, warn.conflicts = FALSE)
library(lubridate, warn.conflicts = FALSE)
library(cowplot)
library(fmsb)
library(hrbrthemes)
library(ggthemes)
library(colormap)

library(ggrepel)

library(plotly)


###source plots
source('r_plots.R')


#setting overlaps for ggrepel
options(ggrepel.max.overlaps = Inf)

df <- read.table(
"data\\fomcMinutesSummary.csv",  ##på detta sätt läser den ur aktuell mapp
  sep=",", header=TRUE)


#Change dates
df <- df %>%
  mutate(date = as.Date(gsub("\\D", "", date), format = "%Y%m%d"))


#arrange
df <- arrange(df, date)



#numrera antal protokoll
temp <- df%>%
  select(date) %>%
  distinct() %>%
  mutate(num = 1:n())

df <- merge(df, temp, by = "date", all.x = TRUE)


###sliding mean
df <- df  %>%
  group_by(subject, additional) %>% 
  mutate(avg_st = slide_index_dbl(frequency, num, mean, .before=4, .after=-1,.complete=T)) %>% ##dont include the current
  mutate(avg_lt = mean(frequency))%>%
  mutate(avg_st_share = slide_index_dbl(frequency_share, num, mean, .before=4, .after=-1,.complete=T))%>%
  mutate(avg_lt_share = mean(frequency_share))%>%
  mutate(ma_3m = slide_index_dbl(frequency, num, mean, .before=2, .after=0, .complete=T))%>%
  mutate(ma_3m_share = slide_index_dbl(frequency_share, num, mean, .before=2, .after=0, .complete=T))


#exclude first three rows to only include when 3m_moving is on
df <-df %>%
  filter(num > 3)

#one minute lag
df <- df %>%
  group_by(subject, additional) %>%
  mutate(previous = lag(frequency, n = 1, default = NA)) %>%
  mutate(previous_share = lag(frequency_share, n = 1, default = NA))



df <- df %>%
  mutate(chg_previous = frequency - previous)%>%
  mutate(chg_avg_st = frequency - avg_st)%>%
  mutate(chg_avg_lt = frequency - avg_lt)%>%
  mutate(chg_previous_share = frequency_share - previous_share)%>%
  mutate(chg_avg_st_share = frequency_share - avg_st_share)%>%
  mutate(chg_avg_lt_share = frequency_share - avg_lt_share)

  






###fed funds rate


df2 <- read.table(
  "data\\fedfundsRate.csv", 
  sep=",", header=TRUE)


#Change dates
df2 <- df2 %>%
  mutate(date = as.Date(gsub("\\D", "", date), format = "%Y%m%d"))


#arrange
df2 <- arrange(df2, date)

df2 <- df2%>%
  filter(bound == "lower_bound")%>%
  select(-bound)



df <- merge(df, df2, by ="date", all.x =  TRUE)

df <- as.data.frame(df)
df[is.na(df)] <- 0

```


```{r, echo=FALSE, results='asis'}
#https://bookdown.org/yihui/rmarkdown-cookbook/results-asis.html
#This is for writing markdown text but grabbing the date from the dataset
header = paste("## Text mining FOMC Minutes", max(df$date))
cat(header)

## Text Mining the Fed 

```



---

FOMC Minutes are usually a hot topic on the financial markets. There are plenty of observeres trying to break down what they said, and what they didn´t say.This project aims to give colour on both the actual context but also (hopefully) the underlying meaning and sentiment. With the field of text mining, this projects breaks down the Minutes into multiple areas making plots out of words.

To be able to to compare Minutes by different length with each other, everything below is set in relation to total the number of words or paragraph in their respective Minutes. Please see *[github](https://github.com/cnordenlow/text-mining-fomc)* for methodology.


**Table of Contents**

* [General sentiment](#general-sentiment) 

* [Economic and financial market conditions](#economic-and-financial-market-conditions-analysis) 

* [Policy toolbox and topics](#policy-toolbox-and-topics) 

* [In deeper breakdown of selected topics](#in-deeper-breakdown) 
 

---




### General sentiment

#### Net sentiment
*Net sentiment is calculated by extracting all positive and negative words, and then taking the difference between these divided by the total number of words.*
```{r, echo=FALSE, messages=FALSE}

#plot spread, average sentiment trending down

temp <- df %>%
  filter(category == "sentiment")%>%
  filter(subject == "net_sentiment")%>%
 # mutate(sign = if_else(chg_avg >= 0, "Positive", "Negative"))  %>%
#  as.data.frame(temp)%>%
  pivot_longer(-c("category", "subject", "additional", "date"), values_to = "values")%>%
  filter(name %in% c("chg_avg_lt_share"))%>%
  mutate(change_positive = values > 0)


c_title = "Net sentiment index"
c_subtitle = "Net sentiment (positive - negative words) vs average"
c_caption = "Source: FOMC Minutes, Loughran-McDonald dicitonary, own calculations."
c_x_axis = ""
c_y_axis = "Sentiment index"



p <- ggplot(data = temp,
            mapping = aes(x = date, y = values, fill = change_positive))+
  geom_col() + guides(fill = FALSE) +
    theme_light()+
  #  theme_minimal(base_size=8)+
  theme(legend.position="bottom",
        plot.caption=element_text(hjust=0),
        plot.subtitle=element_text(face="italic"),
        plot.title=element_text(size=16,face="bold"))+
  labs(x=c_x_axis,y=c_y_axis,
       title=c_title,
       subtitle=c_subtitle,
       caption=c_caption)+
  scale_color_manual(values=c("#d73027","#4575b4"),name="Net sentiment Above/Below moving average sentiment")+
  scale_y_continuous(limits=c(-max(abs(temp$values)),max(abs(temp$values))))
p



```


#### Intensifier index
*Intensifier-index shows the magnitude of the net sentiment by setting positive and negative words in combination with intensifier words (e.g. extremely, significant, sharply etc).*

```{r,echo=FALSE, messages=FALSE}




temp <- df %>%
  filter(category == "intensifiers")%>%
  filter(subject %in% c("intensifiers_net"))%>%
  filter(additional =="count_words")%>%
  
  #for plotting
  mutate(y_axis = ma_3m_share,
         x_axis = date,
         hline_intercept = avg_lt_share,
         fed_funds_rate = rate)



c_title = "Intensifier index"
c_subtitle = "Intensifier-index shows the magnutide of positive and negative words (3m moving avg). \n Long term average in red, fed funds rate in blue (not fit to scale)."
c_caption = "Source: FOMC Minutes, Loughran-McDonald dicitonary, own calculations. \nIntensifier-index calulates the difference between positive and negative words in combination with intensifiers."
c_x_axis = ""
c_y_axis = "Index"





p1 <- plot_line(temp, x_axis, y_axis, hline_intercept, fed_funds_rate, c_title, c_subtitle, c_caption, c_x_axis, c_y_axis)
p1

```


#### Strong-Weak-Moderate - Index

```{r,echo=FALSE, messages=FALSE}




temp <- df %>%
  filter(category == "sentiment_words")%>%
  filter(subject %in% c("Strong", "Weak", "Moderate"))%>%
  filter(additional =="count_words")%>%
  # as.data.frame(temp)%>%
  pivot_longer(-c("category", "subject", "additional", "date"), values_to = "values")%>%
  filter(name %in% c("ma_3m_share"))%>%
  #filter(name %in% c("frequency_share"))%>%
  select(date,subject, values)%>%
  pivot_wider(date, names_from = subject, values_from = values)%>%
  mutate(diff = (Strong-Weak)/Moderate)%>%
  mutate(average = mean(diff))%>%
  mutate(y_axis = diff,
         x_axis = date,
         hline_intercept = average)


##addera fed funds rate###
temp2 <- df %>%
  select(date, rate)%>%
  distinct(date,rate)

temp <- merge(temp,temp2,by.x = "date", all.x = TRUE)

temp <- temp %>%
  mutate(fed_funds_rate = rate)



c_title = "SWM-Index"
c_subtitle = "The use of words strong, weak and moderate in an index. \n Long term average in red, fed funds rate in blue (not fit to scale)."
c_caption = "Source: FOMC Minutes, own calculations. \nIndex: (Strong - weak) / moderate."
c_x_axis = ""
c_y_axis = "SWM-index"



p1 <- plot_line(temp, x_axis, y_axis, hline_intercept, fed_funds_rate, c_title, c_subtitle, c_caption, c_x_axis, c_y_axis)

p1
```


#### Selected sentiment indicators

```{r,echo=FALSE, messages=FALSE}

temp <- df %>%
#  as.data.frame(temp)%>%
  filter(category == "sentiment_words")%>%
  filter(additional == "count_words")%>%
  filter(date == max(df$date))%>%
  select(subject, frequency_share, chg_avg_st_share, chg_avg_lt_share)%>%
  mutate(y_axis = chg_avg_st_share,
         x_axis = chg_avg_lt_share,
         bubble_size = frequency_share)


c_title = "Mapping Feds mind: selected sentiment indicators"
c_subtitle = "Topics current share compared to short and long term average"
c_caption = "Source: FOMC Minutes, own calculations."
c_x_axis = "Difference vs long term average"
c_y_axis = "Difference vs short term average"


p <- plot_bubble(temp, x_axis, y_axis, bubble_size, c_title, c_subtitle, c_caption, c_x_axis, c_y_axis)

p


```



---

### Economic and financial market conditions

#### Economic topics

```{r,echo=FALSE, messages=FALSE}


temp <- df %>%
  #as.data.frame(temp)%>%
  filter(category == "broad_topics")%>%
  filter(additional == "count_words")%>%
  filter(date == max(df$date))%>%
  select(subject, frequency_share, chg_avg_st_share, chg_avg_lt_share)%>%
  mutate(y_axis = chg_avg_st_share,
         x_axis = chg_avg_lt_share,
         bubble_size = frequency_share)



c_title = "Mapping Feds mind: economic topics"
c_subtitle = "Topics current share compared to short and long term average"
c_caption = "Source: FOMC Minutes, own calculations."
c_x_axis = "Difference vs long term average"
c_y_axis = "Difference vs short term average"


#https://gist.github.com/grigory93/f370c5eb997fc74b7b7ec83e73d4dffa#file-ggplot2-data-r

#https://ggrepel.slowkow.com/articles/examples.html

p <- plot_bubble(temp, x_axis, y_axis, bubble_size, c_title, c_subtitle, c_caption, c_x_axis, c_y_axis)

p
  

```


#### Sentiment analysis of economic topics



```{r,echo=FALSE, messages=FALSE}


###################PLOT all in the same. Denna borde man köra på för sentiment per topic?



temp <- df%>%
  filter(category == "broad_topics")%>%
  filter(additional == "net_sentiment_per_topic")%>%
  filter(date >= max(df$date))%>%
  rename("Current sentiment" = "frequency_share",
         "Difference vs short term avg" = "chg_avg_st_share",
         "Difference vs long term avg" = "chg_avg_lt_share",
         )%>%
  #as.data.frame(temp)%>%
  pivot_longer(-c("category", "subject", "additional", "date"), values_to = "values")%>%
  filter(name %in% c("Current sentiment","Difference vs short term avg", "Difference vs long term avg"))%>%
mutate(change_positive = values >= 0)
  

min_y_scale = min(temp$values) - abs(0.1 * min(temp$values))
max_y_scale = max(temp$values) + abs(0.1 * max(temp$values))


temp$group <- factor(temp$name, levels = c("Current sentiment","Difference vs short term avg", "Difference vs long term avg")) ##This is needed to keep the order



c_title = "Sentiment per topic"
c_subtitle = "Net sentiment (positive - negative words) for each topic."
c_caption = "Source: FOMC Minutes, Loughran-McDonald dicitonary, own calculations."
c_x_axis = "Topic"
c_y_axis = "Net sentiment per topic"


######Help for ordering after first plots values
temp <- temp %>%
  mutate(order = ifelse(name == "Current sentiment", values,0))%>%
  arrange(order, values)


plot <- ggplot(data = temp,
               #   aes(x = subject, y = values,
               aes(x = reorder(subject, order), y = values,
                   fill = change_positive))+
  geom_bar(stat = "identity")+
  coord_flip()+
  
      labs(x=c_x_axis,y=c_y_axis,
       title=c_title,
       subtitle=c_subtitle,
       caption=c_caption)+
  
  theme_light()+
  theme(
      strip.background =element_blank(),  
      legend.position="bottom",
      plot.caption=element_text(hjust=0),
      plot.subtitle=element_text(face="italic"),
      plot.title=element_text(size=16,face="bold"))+
  
  theme(strip.text = element_text(colour = 'black', face = 'bold'))+
  guides(fill = FALSE)+
  #ylab("") +
  xlab("") +
  facet_wrap(~group, scales = "free_x")+
  scale_y_continuous(limits=c(min_y_scale,max_y_scale))

plot


```



#### Financial markets

```{r,echo=FALSE, messages=FALSE}


temp <- df %>%
  #as.data.frame(temp)%>%
  filter(category == "financial_conditions")%>%
  filter(additional == "count_words")%>%
  filter(date == max(df$date))%>%
  select(subject, frequency_share, chg_avg_st_share, chg_avg_lt_share)%>%
  mutate(y_axis = chg_avg_st_share,
         x_axis = chg_avg_lt_share,
         bubble_size = frequency_share)



c_title = "Mapping Feds mind: financial markets"
c_subtitle = "Topics current share compared to short and long term average"
c_caption = "Source: FOMC Minutes, own calculations."
c_x_axis = "Difference vs long term average"
c_y_axis = "Difference vs short term average"



p <- plot_bubble(temp, x_axis, y_axis, bubble_size, c_title, c_subtitle, c_caption, c_x_axis, c_y_axis)

p

#https://gist.github.com/grigory93/f370c5eb997fc74b7b7ec83e73d4dffa#file-ggplot2-data-r


```



#### Sentiment analysis of financial markets



```{r,echo=FALSE, messages=FALSE}


###################PLOT all in the same. Denna borde man köra på för sentiment per topic?



temp <- df%>%
  filter(category == "financial_conditions")%>%
  filter(additional == "net_sentiment_per_topic")%>%
  filter(date >= max(df$date))%>%
  rename("Current sentiment" = "frequency_share",
         "Difference vs short term avg" = "chg_avg_st_share",
         "Difference vs long term avg" = "chg_avg_lt_share",
         )%>%
  #as.data.frame(temp)%>%
  pivot_longer(-c("category", "subject", "additional", "date"), values_to = "values")%>%
  filter(name %in% c("Current sentiment","Difference vs short term avg", "Difference vs long term avg"))%>%
mutate(change_positive = values >= 0)
  

min_y_scale = min(temp$values) - abs(0.1 * min(temp$values))
max_y_scale = max(temp$values) + abs(0.1 * max(temp$values))


temp$group <- factor(temp$name, levels = c("Current sentiment","Difference vs short term avg", "Difference vs long term avg")) ##This is needed to keep the order



c_title = "Sentiment per topic"
c_subtitle = "Net sentiment (positive - negative words) for each topic."
c_caption = "Source: FOMC Minutes, own calculations."
c_x_axis = "Topic"
c_y_axis = "Net sentiment per topic"


######Help for ordering after first plots values
temp <- temp %>%
  mutate(order = ifelse(name == "Current sentiment", values,0))%>%
  arrange(order, values)


plot <- ggplot(data = temp,
               #   aes(x = subject, y = values,
               aes(x = reorder(subject, order), y = values,
                   fill = change_positive))+
  geom_bar(stat = "identity")+
  coord_flip()+
  
      labs(x=c_x_axis,y=c_y_axis,
       title=c_title,
       subtitle=c_subtitle,
       caption=c_caption)+
  
  theme_light()+
#  theme(strip.background =element_blank(),
 #       panel.grid.minor.x = element_blank(),
  #      panel.grid.minor.y = element_blank())+
  theme(
      strip.background =element_blank(),  
      legend.position="bottom",
      plot.caption=element_text(hjust=0),
      plot.subtitle=element_text(face="italic"),
      plot.title=element_text(size=16,face="bold"))+
  
  theme(strip.text = element_text(colour = 'black', face = 'bold'))+
  guides(fill = FALSE)+
  #ylab("") +
  xlab("") +
  facet_wrap(~group, scales = "free_x")+
  scale_y_continuous(limits=c(min_y_scale,max_y_scale))

plot


```



---

### Policy toolbox and topics

#### Policy toolbox

```{r,echo=FALSE, messages=FALSE}


temp <- df %>%
 # as.data.frame(temp)%>%
  filter(category == "policy_topics")%>%
  filter(additional == "count_words")%>%
  filter(date == max(df$date))%>%
  select(subject, frequency_share, chg_avg_st_share, chg_avg_lt_share)%>%
  mutate(y_axis = chg_avg_st_share,
         x_axis = chg_avg_lt_share,
         bubble_size = frequency_share)


c_title = "Mapping Feds mind: policy toolbox"
c_subtitle = "Topics current share compared to short and long term average"
c_caption = "Source: FOMC Minutes, own calculations."
c_x_axis = "Difference vs long term average"
c_y_axis = "Difference vs short term average"

#https://gist.github.com/grigory93/f370c5eb997fc74b7b7ec83e73d4dffa#file-ggplot2-data-r


p <- plot_bubble(temp, x_axis, y_axis, bubble_size, c_title, c_subtitle, c_caption, c_x_axis, c_y_axis)

p


```





#### Policy key words

```{r,echo=FALSE, messages=FALSE}
temp <- df %>%
#  as.data.frame(temp)%>%
  filter(category == "policy_words")%>%
  filter(additional == "count_words")%>%
  filter(date == max(df$date))%>%
  select(subject, frequency_share, chg_avg_st_share, chg_avg_lt_share)%>%
  mutate(y_axis = chg_avg_st_share,
         x_axis = chg_avg_lt_share,
         bubble_size = frequency_share)



c_title = "Mapping Feds mind: policy key words"
c_subtitle = "Topics current share compared to short and long term average"
c_caption = "Source: FOMC Minutes, own calculations."
c_x_axis = "Difference vs long term average"
c_y_axis = "Difference vs short term average"


p <- plot_bubble(temp, x_axis, y_axis, bubble_size, c_title, c_subtitle, c_caption, c_x_axis, c_y_axis)

p

#https://gist.github.com/grigory93/f370c5eb997fc74b7b7ec83e73d4dffa#file-ggplot2-data-r

#https://ggrepel.slowkow.com/articles/examples.html






```






#### Key-words-O-Meters
```{r,echo=FALSE, messages=FALSE}

###Accommodative

temp <- df %>%
  filter(category == "policy_words")%>%
  filter(subject == "Accommodative")%>%
  filter(additional =="count_words")%>%
  
#for plotting
        mutate(y_axis = ma_3m_share,
         x_axis = date,
        hline_intercept = avg_lt_share,
        fed_funds_rate = rate)



c_title = "Accommodative-O-Meter"
c_subtitle = "The use of the word accommodative (3m moving avg). \nLong term average in red, fed funds rate in blue (not fit to scale)."
c_caption = "Source: FOMC Minutes, own calculations."
c_x_axis = ""
c_y_axis = "Share of paragraphs"



d1 <- plot_line(temp, x_axis, y_axis, hline_intercept, fed_funds_rate, c_title, c_subtitle, c_caption, c_x_axis, c_y_axis)


###Normalization

temp <- df %>%
  filter(category == "policy_words")%>%
  filter(subject == "Normalization")%>%
  filter(additional =="count_words")%>%
  
#for plotting
        mutate(y_axis = ma_3m_share,
         x_axis = date,
        hline_intercept = avg_lt_share,
        fed_funds_rate = rate)



c_title = "Normalization-O-Meter"
c_subtitle = "The use of the word normalization (3m moving avg). \nLong term average in red, fed funds rate in blue (not fit to scale)."
c_caption = "Source: FOMC Minutes, own calculations."
c_x_axis = ""
c_y_axis = "Share of paragraphs"



d2 <- plot_line(temp, x_axis, y_axis, hline_intercept, fed_funds_rate, c_title, c_subtitle, c_caption, c_x_axis, c_y_axis)



###Gradual

temp <- df %>%
  filter(category == "policy_words")%>%
  filter(subject == "Gradual")%>%
  filter(additional =="count_words")%>%
  
#for plotting
        mutate(y_axis = ma_3m_share,
         x_axis = date,
        hline_intercept = avg_lt_share,
        fed_funds_rate = rate)



c_title = "Gradual-O-Meter"
c_subtitle = "The use of the word gradual (3m moving avg). \nLong term average in red, fed funds rate in blue (not fit to scale)."
c_caption = "Source: FOMC Minutes, own calculations."
c_x_axis = ""
c_y_axis = "Share of paragraphs"



d3 <- plot_line(temp, x_axis, y_axis, hline_intercept, fed_funds_rate, c_title, c_subtitle, c_caption, c_x_axis, c_y_axis)




###Gradual

temp <- df %>%
  filter(category == "policy_words")%>%
  filter(subject == "Data dependent")%>%
  filter(additional =="count_words")%>%
  
#for plotting
        mutate(y_axis = ma_3m_share,
         x_axis = date,
        hline_intercept = avg_lt_share,
        fed_funds_rate = rate)



c_title = "Data-Dependent-O-Meter"
c_subtitle = "The use of the meaning of data dependent (3m moving avg). \nLong term average in red, fed funds rate in blue (not fit to scale)."
c_caption = "Source: FOMC Minutes, own calculations."
c_x_axis = ""
c_y_axis = "Share of paragraphs"



d4 <- plot_line(temp, x_axis, y_axis, hline_intercept, fed_funds_rate, c_title, c_subtitle, c_caption, c_x_axis, c_y_axis)


d1
d2
d3
#d4
#library(gridExtra)
#grid.arrange(d1, d2, ncol = 2)    
#grid.arrange(d3, ncol = 2)    


```



#### Policy action
*The graph below show the difference between sentences containing words like consensus, majority, all and those of words like a few, one or two. Above red dotted line suggest there are a more consensus view among participants then when below the dotted red line.*

```{r,echo=FALSE, messages=FALSE}


temp <- df %>%
  filter(category == "quantitative_words")%>%
  filter(subject %in% c("Consensus", "Few"))%>%
  filter(additional =="count_words")%>%
  #as.data.frame(temp)%>%
  pivot_longer(-c("category", "subject", "additional", "date"), values_to = "values")%>%
  #filter(name %in% c("frequency_share"))%>%
  filter(name %in% c("ma_3m_share"))%>%
  
  select(date,subject, values)%>%
  pivot_wider(date, names_from = subject, values_from = values)%>%
  mutate(diff = Consensus-Few)%>%
  mutate(average = mean(diff))%>%
    mutate(y_axis = diff,
         x_axis = date,
        hline_intercept = average)









##add fed funds rate
temp2 <- df %>%
  select(date, rate)%>%
  distinct(date,rate)

temp <- merge(temp,temp2,by.x = "date", all.x = TRUE)

temp <- temp %>%
  mutate(fed_funds_rate = rate)




c_title = "Consensus-O-Meter"
c_subtitle = "The difference between the meaning of consensus and a few (3m moving avg). \nLong term average in red, fed funds rate in blue (not fit to scale)."
c_caption = "Source: FOMC Minutes, own calculations."
c_x_axis = ""
c_y_axis = "Relative"



p1 <- plot_line(temp, x_axis, y_axis, hline_intercept, fed_funds_rate, c_title, c_subtitle, c_caption, c_x_axis, c_y_axis)
p1



```




### In deeper breakdown 

#### Inflation
```{r,echo=FALSE, messages=FALSE}
temp <- df %>%
#  as.data.frame(temp)%>%
  filter(category == "in_deep_inflation")%>%
  filter(additional == "count_words")%>%
  filter(date == max(df$date))%>%
  select(subject, frequency_share, chg_avg_st_share, chg_avg_lt_share)%>%
  mutate(y_axis = chg_avg_st_share,
         x_axis = chg_avg_lt_share,
         bubble_size = frequency_share)



c_title = "Mapping Feds mind: inflation"
c_subtitle = "Topics current share compared to short and long term average"
c_caption = "Source: FOMC Minutes, own calculations."
c_x_axis = "Difference vs long term average"
c_y_axis = "Difference vs short term average"

p <- plot_bubble(temp, x_axis, y_axis, bubble_size, c_title, c_subtitle, c_caption, c_x_axis, c_y_axis)

p
#https://gist.github.com/grigory93/f370c5eb997fc74b7b7ec83e73d4dffa#file-ggplot2-data-r

#https://ggrepel.slowkow.com/articles/examples.html





```


#### Labor market
```{r,echo=FALSE, messages=FALSE}
temp <- df %>%
#  as.data.frame(temp)%>%
  filter(category == "in_deep_labor")%>%
  filter(additional == "count_words")%>%
  filter(date == max(df$date))%>%
  select(subject, frequency_share, chg_avg_st_share, chg_avg_lt_share)%>%
  mutate(y_axis = chg_avg_st_share,
         x_axis = chg_avg_lt_share,
         bubble_size = frequency_share)



c_title = "Mapping Feds mind: labor market"
c_subtitle = "Topics current share compared to short and long term average"
c_caption = "Source: FOMC Minutes, own calculations."
c_x_axis = "Difference vs long term average"
c_y_axis = "Difference vs short term average"

p <- plot_bubble(temp, x_axis, y_axis, bubble_size, c_title, c_subtitle, c_caption, c_x_axis, c_y_axis)

p








```

#### Asset purchases
```{r,echo=FALSE, messages=FALSE}
temp <- df %>%
#  as.data.frame(temp)%>%
  filter(category == "in_deep_asset_program")%>%
  filter(additional == "count_words")%>%
  filter(date == max(df$date))%>%
  select(subject, frequency_share, chg_avg_st_share, chg_avg_lt_share)%>%
  mutate(y_axis = chg_avg_st_share,
         x_axis = chg_avg_lt_share,
         bubble_size = frequency_share)



c_title = "Mapping Feds mind: asset purchases"
c_subtitle = "Topics current share compared to short and long term average"
c_caption = "Source: FOMC Minutes, own calculations."
c_x_axis = "Difference vs long term average"
c_y_axis = "Difference vs short term average"


p <- plot_bubble(temp, x_axis, y_axis, bubble_size, c_title, c_subtitle, c_caption, c_x_axis, c_y_axis)

p


  
  





```

